\tool: Revisiting BadUSB with Type-C

### 2021-03-07 WOOT/Files/background.tex
Update

%\noindent\outline{Security Problem}\\
During the development of \ac{USB} specification, security was rarely considered. As
the \ac{USB}-IF believes it is the duty of \acp{OEM}
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

%\fengwei{FIXME: add a reference for each attack in the Table.}
%\fengwei{FIXME: The table is too wide, exceeds the max size.}
\begin{table*}
\begin{tabular}{|c|l|c|c|c|}
	\hline
	\textbf{Year} & \textbf{Protocol Version} & \textbf{Supported Peripherals} & \textbf{Transfer Speed} & \textbf{Attacks} \\
	\hline
	1996 & \ac{USB} 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & \ac{HID} Emulating (BadUSB)~\cite{badusb} \\
	\hline
	2000 & \ac{USB} 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
	\hline
	2008 & \ac{USB} 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
	\hline
	2013 & \ac{USB} 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
	\hline
	2017 & \ac{USB} 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{\ac{USB} Protocol Timeline.}
\label{table:usb_timeline}
\end{table*}

>>>>

%\noindent\outline{Security Problem}\\
During the development of \ac{USB} specification, security was considered insufficiently~\cite{sok}. As
the \ac{USB}-IF believes it is the duty of \acp{OEM}
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

%\fengwei{FIXME: add a reference for each attack in the Table.}
%\fengwei{FIXME: The table is too wide, exceeds the max size.}
\begin{table*}
\begin{tabular}{|c|l|c|c|c|}
	\hline
	\textbf{Year} & \textbf{Protocol Version} & \textbf{Supported Peripherals} & \textbf{Transfer Speed} & \textbf{Attacks} \\
	\hline
	1996 & \ac{USB} 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & \ac{HID} Emulation (BadUSB)~\cite{badusb} \\
	\hline
	2000 & \ac{USB} 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
	\hline
	2008 & \ac{USB} 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
	\hline
	2013 & \ac{USB} 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
	\hline
	2017 & \ac{USB} 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{\ac{USB} Protocol Timeline.}
\label{table:usb_timeline}
\end{table*}

### 2021-03-07 WOOT/Files/introduction.tex
Update

On the other side of the coin, the security of \ac{USB} has caused serious problems.
The designers of the \ac{USB} protocol did not care much about security issues as
they wanted to make an easy-to-use protocol.  There are more than four hundred
vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

@@

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers can not obtain the current \ac{UI} status which limits
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns like buttons and links on victim
computers by disguising \ac{USB} devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the usage of the host network.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a larger range of
peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

>>>>

On the other side of the coin, the security of \ac{USB} has caused serious problems.
The designers of the \ac{USB} protocol did not care much about security issues as
they wanted to make an easy-to-use protocol.  There are more than 400
vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

@@

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status which limits
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns like buttons and links on victim
computers by disguising \ac{USB} devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the usage of the host network.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a larger range of
peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

### 2021-03-07 WOOT/Files/related_work.tex
Update

% Using USB devices to inject code
Besides attacking from the protocol perspective, previous works use a
\ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
rootkit to hide malicious files on the \ac{USB} storage device, \cite{flame} uses a
zero-day exploit and malicious \textit{autorun.inf} to execute the malware
automatically. There are also works like \cite{brain,stuxnet,conficker}
following the same paradigm and performing code-injection attacks. These
attacks are much more damaging and flexible,
but they require certain existing flaws like a \cite{zero-day} vulnerability and \ac{USB} is merely
a payload delivery method.

@@

It is worth noting that our \tool is different from JFC~\cite{JFC}. Juice Filming Attacks can not control the attacked device, it can only video-capture user inputs during charging. However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.

@@

From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a \ac{USB} cable. Based
on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leaving power pins intact. However, this method poses
a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
stops all \ac{USB} functions other than charging.

>>>>

% Using USB devices to inject code
Besides attacking from the protocol perspective, previous works use a
\ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
rootkit to hide malicious files on the \ac{USB} storage device, \cite{flame} uses a
zero-day exploit and malicious \textit{autorun.inf} to execute the malware
automatically. There are also works like \cite{brain,stuxnet,conficker}
following the same paradigm and performing code-injection attacks. These
attacks are much more damaging and flexible,
but they require certain existing flaws like a zero-day vulnerability\cite{zero-day}  and \ac{USB} is merely
a payload delivery method.

@@

It is worth noting that our \tool is different from JFC~\cite{JFC}. Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging. However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.

@@

From the hardware perspective, the BadUSB attack requires \mbox{`D-' and `D+'} pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a \ac{USB} cable. Based
on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving power pins intact. However, this method poses
a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
stops all \ac{USB} functions other than charging.
